---
title: "R Notebook"
output: html_notebook
author: "Sweta Sharma"
Date: "09/19/2019"
---

## 1. CSV file for students taking exams, in which rows are students and columns are exams

### Changing the present working directory

```{r}
setwd("/Users/swetasharma/Documents/Sweta/Sem_1/Statistics with R/Hw_2/")
```

### Exporting student exam data from csv
```{r}
# Read CSV into R data frame
stu_sub_data <- read.csv(file="stu_subject.csv", header=FALSE, sep=",")
stu_sub_data
```

## 2. CSV file for exam time slots, in which rows are exams and columns are timeslots
```{r}
# Read CSV into R data frame
sub_time_data <- read.csv(file="sub_timeslot.csv", header=FALSE, sep=",")
sub_time_data
```
```{r}
class(sub_time_data)
```

## 3. R code to convert dataframe to 2 matrices

```{r}
stu_sub_matrix <- as.matrix(stu_sub_data)
row.names(stu_sub_matrix) <- c("stu1","stu2","stu3","stu4")
colnames(stu_sub_matrix) <- c("sub1","sub2","sub3","sub4","sub5")
stu_sub_matrix
```
```{r}
sub_time_matrix <- as.matrix(sub_time_data)
row.names(sub_time_matrix) <- c("sub1","sub2","sub3","sub4","sub5")
colnames(sub_time_matrix) <- c("slot1","slot2","slot3","slot4")
sub_time_matrix
```
```{r}
class(sub_time_data)
```
## 4. Compute an exam schedule matrix
### Multiplying the matrices to create a schedule
```{r}
stu_slot_schedule <- stu_sub_matrix %*% sub_time_matrix
stu_slot_schedule
```
```{r}
class(stu_slot_schedule)
```

### Converting schedule matrix, stu_slot_schedule, to a data frame
```{r}
df_stu_slot_schedule <- as.data.frame(stu_slot_schedule)
df_stu_slot_schedule
# Confirming class of data frame df_stu_slot_schedule
class(df_stu_slot_schedule)
```

### Writing data frame to a csv file
```{r}
# Write data frame to a CSV
write.csv(df_stu_slot_schedule, file = "stu_slot.csv")
```

## 5. R UDF function that computes the number of direct conflicts in the resulted schedule matrix
### UDF function to find the number of conflicts


```{r}
count_conflict = function(x)
{
   return(length(x[x >= 2]))
}

count_conflict(stu_slot_schedule)
#length((stu_slot_schedule[stu_slot_schedule >= 2]))
#stu_slot_schedule[stu_slot_schedule[,] >=2 ]
```

## 6. R function for optimal slot

### Create compute_optimal_matrix UDF where k is the no of times schedule matrix will be randomly generated
```{r}

compute_optimal_matrix = function(k)
{
for(x in 1:k){
# Random assign 0 or 1 to sub_time_matrix

  r <- 5
  c <- 4
  sub_time_random <- matrix(0, r, c)
  for(i in 1:r){
      for(j in 1:c){
        sub_time_random[i, j] <- sample(c(0,1),1)
      }
  }

  row.names(sub_time_random) <- c("r_sub1", "r_sub2", "r_sub3", "r_sub4", "r_sub5")
  colnames(sub_time_random) <- c("r_slot1", "r_slot2", "r_slot3", "r_slot4")

  # Multiply matrices to create a schedule

  stu_slot_random <- stu_sub_matrix %*% sub_time_random
  #print(stu_slot_random)

  # Compute the no of conflicts
  if(x ==1){
      conflict_number <- count_conflict(stu_slot_random)
      #rint("I am in loop 1" )
      #print(conflict_number)
  }
  else{
  
      if(count_conflict(stu_slot_random) < conflict_number){
      conflict_number <- count_conflict(stu_slot_random)
      optimal_matrix <- sub_time_random
      }
  
  }

# Check if the new result is less than last result. if yes, assign matrix to a variable
  
}
# at last print and export variable to csv
print("the optimal count is:")
print(conflict_number)
print("the optimal matrix is:")
print(optimal_matrix)
df_optimal_matrix <- as.data.frame(optimal_matrix)
write.csv(df_optimal_matrix, file = "optimal_stu_slot.csv")
}
```
## calling compute_optimal_matrix function
```{r}
compute_optimal_matrix(100)
```

